PomBase data export

### 2025-03-12 PomBase_data_export.Rmd
Only export complement comparison for curation

---
title: "PomBase data export"
author: "Charlotte Soneson, Michael Stadler, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
        self_contained: true
params:
    rds150: "data/ipms_150_sce.rds"
    rds500: "data/ipms_500_sce.rds"
    peakcsv: "data/fused_peaks_filtered.csv.gz"
    baitclass: "data/ipms_bait_class.txt"
    idmap: "data/id_mapping_table.txt"
    motifrds: "data/motifs_annotated.rds"
    gtffile: "reference/Schizosaccharomyces_pombe.ASM294v2.55.gtf"
---

@@

## IP-MS data
sce150 <- readRDS(params$rds150)
sce500 <- readRDS(params$rds500)

@@

Table of proteins pulled-down by each TF at low salt and high salt conditions.

```{r export-ip-ms, class.source="fold-show"}
testL150 <- metadata(sce150)$testres$tests
res150 <- do.call(bind_rows, lapply(names(testL150), function(nm) {
    testL150[[nm]] |>
        dplyr::filter(adj.P.Val < 0.05 & logFC > 1) |>
        dplyr::select(pid, adj.P.Val, logFC) |>
        dplyr::rename(prey = pid) |>
        dplyr::mutate(bait = .getProteinNameFromComparison(nm))
})) |>
    dplyr::filter(bait != prey) |>
    dplyr::filter(!bait %in% baitclass$Gene_name[baitclass$class == "nobait"]) |>
    dplyr::select(bait, prey, adj.P.Val, logFC)

@@

testL500 <- metadata(sce500)$testres$tests
res500 <- do.call(bind_rows, lapply(names(testL500), function(nm) {
    testL500[[nm]] |>
        dplyr::filter(adj.P.Val < 0.05 & logFC > 1) |>
        dplyr::select(pid, adj.P.Val, logFC) |>
        dplyr::rename(prey = pid) |>
        dplyr::mutate(bait = .getProteinNameFromComparison(nm))
})) |>
    dplyr::filter(bait != prey) |>
    dplyr::filter(!bait %in% baitclass$Gene_name[baitclass$class == "nobait"]) |>
    dplyr::select(bait, prey, adj.P.Val, logFC)

@@

>>>>

---
title: "PomBase data export"
author: "Charlotte Soneson, Michael Stadler, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
        self_contained: true
params:
    rds150: "data/ipms_150_sce.rds"
    rds500: "data/ipms_500_sce.rds"
    rds150untag: "data/ipms_150_untag_sce.rds"
    peakcsv: "data/fused_peaks_filtered.csv.gz"
    baitclass: "data/ipms_bait_class.txt"
    idmap: "data/id_mapping_table.txt"
    motifrds: "data/motifs_annotated.rds"
    gtffile: "reference/Schizosaccharomyces_pombe.ASM294v2.55.gtf"
---

@@

## IP-MS data
sce150 <- readRDS(params$rds150)
sce500 <- readRDS(params$rds500)
sce150untag <- readRDS(params$rds150untag)

@@

Table of proteins pulled-down by each TF at low salt and high salt conditions, 
in comparisons to the broad complement group.

```{r export-ip-ms, class.source="fold-show"}
testL150 <- metadata(sce150)$testres$tests
# exclude highsaltcompl comparisons
testL150 <- testL150[grep("_vs_compl_", names(testL150), value = TRUE)]
# only keep plate Atf1 comparison
testL150 <- testL150[names(testL150) != "Atf1_150_tube_vs_compl_Atf1_150_tube"]
length(testL150)
res150 <- do.call(bind_rows, lapply(names(testL150), function(nm) {
    testL150[[nm]] |>
        dplyr::filter(adj.P.Val < 0.05 & logFC > 1) |>
        dplyr::select(pid, adj.P.Val, logFC) |>
        dplyr::rename(prey = pid) |>
        dplyr::mutate(bait = .getProteinNameFromComparison(nm))
})) |>
    dplyr::filter(bait != prey) |>
    dplyr::filter(!bait %in% baitclass$Gene_name[baitclass$class == "nobait"]) |>
    dplyr::select(bait, prey, adj.P.Val, logFC)

@@

testL500 <- metadata(sce500)$testres$tests
length(testL500)
res500 <- do.call(bind_rows, lapply(names(testL500), function(nm) {
    testL500[[nm]] |>
        dplyr::filter(adj.P.Val < 0.05 & logFC > 1) |>
        dplyr::select(pid, adj.P.Val, logFC) |>
        dplyr::rename(prey = pid) |>
        dplyr::mutate(bait = .getProteinNameFromComparison(nm))
})) |>
    dplyr::filter(bait != prey) |>
    dplyr::filter(!bait %in% baitclass$Gene_name[baitclass$class == "nobait"]) |>
    dplyr::select(bait, prey, adj.P.Val, logFC)

@@

Table of proteins pulled-down by each TF at low salt condition, 
in comparisons to the untagged controls.

```{r}
testL150untag <- metadata(sce150untag)$testres$tests
# only keep plate Atf1 comparison
testL150untag <- testL150untag[names(testL150untag) != 
                                   "Atf1_150_tube_vs_Untagged_150_tube"]
length(testL150untag)
res150untag <- do.call(bind_rows, lapply(names(testL150untag), function(nm) {
    testL150untag[[nm]] |>
        dplyr::filter(adj.P.Val < 0.05 & logFC > 1) |>
        dplyr::select(pid, adj.P.Val, logFC) |>
        dplyr::rename(prey = pid) |>
        dplyr::mutate(bait = .getProteinNameFromComparison(nm))
})) |>
    dplyr::filter(bait != prey) |>
    dplyr::filter(!bait %in% baitclass$Gene_name[baitclass$class == "nobait"]) |>
    dplyr::select(bait, prey, adj.P.Val, logFC)

write.table(res150untag, file = "PomBase/ipms_150mM_vs_untagged_pulldowns.csv", 
            row.names = FALSE, col.names = TRUE, sep = ",", quote = FALSE)
```
